Birth Spacing in the Presence of Son Preference and Sex-Selective \\ Abortions: India's Experience over Four Decades

### 2018-04-19 presentations/2018-paa-poster.tex
Begin adding tables of results

\usepackage{fontspec}
\setsansfont[Ligatures=TeX]{Gandhi Sans}
% \usepackage{unicode-math}
% \setmathfont{TeX Gyre Pagella Math}

@@

@@

\begin{enumerate}
\item there has been a general increase in the length of spacing between births
over the four decades covered by the data.
The exception is for first births, where the median duration has either
remained the same or slightly declined, although this hides a
significant compression of the variation in spell length.

\item the most substantial increase in spacing is for the women who
are most likely to use sex selection.
Among the best-educated women, those with no boys now has 
significantly longer spacing---and a more male-biased sex ratio---than 
similar women with boys.

\item women with no education still follow the standard pattern of
short spacing when they have girls and little evidence of the use of sex
selection.
In other words, these women adhere to a strategy where they achieve a
son through higher fertility rather than the use of sex selection.

\item sex ratios are the most likely to decline within spells at
lower-order spells, where the pressure to provide a son is smaller, and
are more likely to increase or remain consistently high for higher-order
spells, where the pressure to ensure a son is high.

>>>>

\usepackage{fontspec}
\setsansfont[Ligatures=TeX]{Gandhi Sans}
% \usepackage{unicode-math}
% \setmathfont{TeX Gyre Pagella Math}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}

\newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
\newcommand{\X}{$\times$ }
\newcommand{\hs}{\hspace{15pt}}

@@

\begin{table}[hp!]
\begin{center}
\begin{scriptsize}
\begin{threeparttable}
\caption{Estimated Median Duration and Sex Ratio for Rural Women with No Education}
\label{tab:median_sex_ratio_low}
\begin{tabular}{@{} c l D{.}{.}{2.3} D{.}{.}{2.3}  D{.}{.}{2.3} D{.}{.}{2.3} @{}}
\toprule
                   &                            & \mct{1972--1984}                                    & \mct{2005--2016}                                      \\ \cmidrule(lr){3-4} \cmidrule(lr){5-6} 
                   & \mco{Composition of}       & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}   & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}     \\ 
 \mco{Spell}       & \mco{Prior Children}       & \mco{(Months)}  & \mco{Boys}                        & \mco{(Months)}  & \mco{Boys}                          \\ \midrule
\multirow[c]{2}{*}{1} &                            &    26.2       &    52.1^{**}  &    24.4       &    51.5        \\
                      &                            &    (0.2)      &    (0.3)      &    (0.1)      &    (0.4)       \\
\addlinespace 
\multirow[c]{3}{*}{2} & \mco{One girl}             &    18.5       &    51.1       &    19.7       &    51.8        \\
                      &                            &    (0.2)      &    (0.6)      &    (0.2)      &    (0.6)       \\
                      & \mco{One boy}              &    19.6^{***} &    52.7^{**}  &    20.1^{*}   &    52.2^{*}    \\
                      &                            &    (0.1)      &    (0.7)      &    (0.2)      &    (0.5)       \\
\addlinespace 
\multirow[c]{5}{*}{3} & \mco{Two girls}            &    17.9       &    49.4^{*}   &    20.3       &    52.9^{**}   \\
                      &                            &    (0.3)      &    (1.0)      &    (0.2)      &    (0.7)       \\
                      & \mco{One boy / one girl}   &    19.1^{***} &    53.0^{**}  &    21.1^{***} &    51.8        \\
                      &                            &    (0.2)      &    (0.7)      &    (0.2)      &    (0.6)       \\
                      & \mco{Two boys}             &    19.1^{***} &    51.4       &    22.0^{***} &    50.9        \\
                      &                            &    (0.2)      &    (0.9)      &    (0.3)      &    (0.8)       \\
\addlinespace 
\bottomrule
\end{tabular}
\begin{tablenotes} 
\tiny
\item \hspace*{-0.5em} \textbf{Note.}
Bootstrapped standard errors shown in parentheses.
\item[a] For spells two and higher duration sex compositions other than all girls are 
tested against the duration for all girls, with *** indicating significantly different 
at the 1\% level, ** at the 5\% level, and * at the 10\% level, based on bootstrapped
differences.
\item[b] The predicted percent boys is tested against the natural percentage boys, 105 boys per 100 girls,
with *** indicating significantly different at the 1\% level, ** at the 5\% level, 
and * at 10\% level.
\end{tablenotes}
\end{threeparttable}
\end{scriptsize}
\end{center}
\end{table}

@@

\begin{enumerate}
\item There has been a general increase in the length of spacing between births
over the four decades covered by the data.
The exception is for first births, where the median duration has either
remained the same or slightly declined, although this hides a
significant compression of the variation in spell length.

\item The most substantial increase in spacing is for the women who
are most likely to use sex selection.
Among the best-educated women, those with no boys now has 
significantly longer spacing---and a more male-biased sex ratio---than 
similar women with boys.

\item Women with no education still follow the standard pattern of
short spacing when they have girls and little evidence of the use of sex
selection.
In other words, these women adhere to a strategy where they achieve a
son through higher fertility rather than the use of sex selection.

\item Sex ratios are the most likely to decline within spells at
lower-order spells, where the pressure to provide a son is smaller, and
are more likely to increase or remain consistently high for higher-order
spells, where the pressure to ensure a son is high.
